---
title: "OptiVisT AIBox Analysis"
author: "Florian Pätzold"
date: "11/02/2025"
output:
  html_document: default
  pdf_document: default
---

# 1. Setup

Set up the document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE) # for debugging
```

Import all necessary packages.

```{r, echo=FALSE}
library(tidyverse) # ggplot2, tibble, tidyr, readr, purrr, dplyr, stringr, forcats
library(scales) # ggplot default color palette
library(e1071) # skewness and kurtosis
library(ggcorrplot) # correlation
```

Load all the data.

```{r}
# Set working directory to the folder containing the CSV files
base_dir <- getwd()
grasping_data <- read_csv(paste0(base_dir, "/grasping/combined_grasping.csv")) %>% mutate(task = 'grasping')
multiple_objects_data <- read_csv(paste0(base_dir, "/multiple_objects/combined_multiple_objects.csv")) %>% mutate(task = 'multiple_objects')
depth_navigation_data <- read_csv(paste0(base_dir, "/depth_navigation/combined_depth_navigation.csv")) %>% mutate(task = 'depth_navigation')

data_reconstructed <- rbind(grasping_data, multiple_objects_data, depth_navigation_data)

# View sample of the combined data
data_reconstructed %>% sample_n(10)
```

# 2. Data Preprocessing

## 2.1 Data Engineering

```{r}
detection_frame_drop_threshold = 10 # ~40fps average --> 0.25s
tracking_position_threshold = 90 # in a 640x480p output video, this corresponds roughly to a 15% shift on the x-axis (threshold measured from multiple_objects_p1 video)

data_engineered <- data_reconstructed %>% 
  mutate(
    outcome = ifelse(key == 'y', "success", 
              ifelse(key == 'n', "participant_fail", 
              ifelse(key == 'f', "navigation_fail", 
              ifelse(key == 't', "detection_fail", "aborted")))),
              
    trial_duration = end_time - start_time,
    navigation_duration = grasping_time - navigation_time,
    freezing_onset_duration = grasping_time - freezing_time,
    
    # Convert detection to numeric and compute detection rate
    detection = lapply(detection, function(x) as.numeric(unlist(strsplit(x, ",")))),
    detection_rate = sapply(detection, function(x) if (length(x) > 0) sum(x, na.rm = TRUE) / length(x) else NA),
    
    # Count detection drops if lost for X consecutive frames
    detection_drops = sapply(detection, function(x) sum(rle(x == 0)$lengths >= detection_frame_drop_threshold, na.rm = TRUE)),
    
    # Convert confidence to numeric and compute average
    confidence = lapply(confidence, function(x) as.numeric(unlist(strsplit(x, ",")))),
    confidence_average = sapply(confidence, function(x) mean(x[x>0], na.rm = TRUE)),
    
    # Convert target_position to numeric and compute position jumps
    target_position = lapply(target_position, function(pos) {
      as.numeric(unlist(strsplit(gsub("\\[|\\]", "", pos), ",")))
    }),
    
    tracking_jumps = sapply(target_position, function(pos) {
      pos_matrix <- matrix(as.numeric(unlist(strsplit(gsub("\\[|\\]", "", pos), ","))), ncol = 2, byrow = TRUE)
      if (nrow(pos_matrix) > 1) {
        sum(abs(diff(pos_matrix[, 1])) > tracking_position_threshold)  # Only check x-coordinates
      } else {
        0  # No jumps if only one frame
      }
    }),
    
    # Convert target_track_id to numeric and compute tracking jumps
    target_track_id = lapply(target_track_id, function(track_ids) {
      as.numeric(unlist(strsplit(track_ids, ",")))
    }),
    
    identification_jumps = sapply(target_track_id, function(track_ids) {
      if (length(track_ids) > 1) sum(diff(track_ids) != 0, na.rm = TRUE) else 0
    }),
    
    num_frames = sapply(target_position, length),
    tracking_rate = ifelse(num_frames > 0, 1 - (tracking_jumps / num_frames), NA),
    identification_rate = ifelse(num_frames > 0, 1 - (identification_jumps / num_frames), NA)
  )

# freezing_time and grasping_time seem to be the same resulting in always 0 for freezing_onset_duration, so we remove it
data_engineered <- data_engineered %>% 
  select(participant_id, task, trial, target, outcome, trial_duration, navigation_duration, 
         confidence_average, detection_drops, detection_rate, tracking_jumps, tracking_rate, 
         identification_jumps, identification_rate)

data_engineered
```

Validating the data using the videos reveals that tracking jumps might occur because of: actual tracking jump between two objects (true positive), tracking jump because of moving the BB during a freeze and then jumping back (also counts), near-grasping jumps that are mostly irrelevant (false positive). During the experiment, if two actual jumps occurred we marked the trial outcome as 'system_fail'. The identification jumps itself do not seem to largely impact the outcome of the trial. 

Trials like P2 T2,8 are perfect examples for participant fails, where this type of fail should drastically reduce as a result of training (learning to interpret perspective and the camera view-grasp relation). These type of trials can mostly be attributed to perspective problems, i.e. receiving grasping signal and then navigating in the wrong direction from there. With the current design of the bracelet we are not able to represent depth using vibration commands and therefore cannot implement this navigation feature in to depth. 


## 2.2 Data Cleaning

Trial 7 from participant 2 in the depth navigation task is a participant fail.

```{r}
data_engineered <- data_engineered %>%
  mutate(outcome = case_when(
    task == 'depth_navigation' & participant_id == 2 & trial == 7 & outcome == "success" ~ "participant_fail",
    TRUE ~ outcome  # Keep other values unchanged
  ))
```

Add trial type to differentiate between guidance signals in depth navigation task.

```{r}

```

We will detect and treat missing values as well as technical false measurements.

```{r}
n_uncleaned <- nrow(data_engineered)

outliers <- rbind(
  # Removes P3 T4, where P confused "no vibrations" with "grasping" but still grasped correct target -> no valid information about P or system
  #data_engineered %>% filter_if(is.numeric, any_vars(is.na(.))), 
  data_engineered %>% filter_if(is.numeric, any_vars(is.infinite(.))),  # Detect infinite values in numeric columns
  data_engineered %>% filter(participant_id < 0),  # No negative participant IDs
  data_engineered %>% filter(trial < 0 | trial > 10),  # No negative trial numbers, and no more than 10
  data_engineered %>% filter(trial_duration < 0)  # Negative trial durations are measurement errors
)
outliers

# Treatment
data <- data_engineered %>% anti_join(outliers, by = colnames(data_engineered))

n_cleaned <- nrow(data)
cat('Rows removed: ', n_uncleaned - n_cleaned)
```

# 3. Analysis

## 3.1 Exploration

### Visualizations

#### Success

```{r}
data %>%
  mutate(
    group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
    task = factor(task, levels = c("grasping", "multiple_objects", "depth_navigation"))
  ) %>%
  group_by(task) %>%
  summarize(success_count = sum(outcome == 'success'), .groups = "drop") %>% 
  mutate(n = rep(40,3))

data %>%
  mutate(
    group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
    task = factor(task, levels = c("grasping", "multiple_objects", "depth_navigation"))
  ) %>%
  group_by(task, group) %>%
  summarize(success_count = sum(outcome == 'success'), .groups = "drop") %>% 
  mutate(n = rep(20,6))

success_task <- data %>%
  mutate(
    group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
    task = factor(task, levels = c("grasping", "multiple_objects", "depth_navigation"))
  ) %>%
  group_by(task, participant_id, group) %>%
  summarize(success_count = sum(outcome == 'success'), .groups = "drop") %>%
  ggplot(aes(x = task, y = (success_count / n_trials) * 100, fill = as.factor(participant_id))) +  
  geom_col(width = 0.75, position = position_dodge(width = 0.75), color = "black") +
  geom_text(aes(label = round((success_count / n_trials) * 100, 2)),  
            position = position_dodge(width = 0.75), vjust = 1.5, size = 3) +
  labs(title = "Success Percentage by Task\n",  
       x = NULL,  
       y = "Success (%)\n",  
       fill = "Expertise") +  
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_fill_manual(values = c("1" = "#fdb338", "2" = "#f7c674", "3" = "#0475d4", "4" = "#3e8dcf"),
                    labels = c("", "Expert", "", "Naive"),
                    #breaks = c("1", "3"), # only possible if labels has same length, i.e. c("Expert", "Naive")
                    guide = guide_legend(
                      byrow = TRUE, 
                      nrow = 2,
                      keywidth = 1, keyheight = 1 # adjust depending on liking
                    )) + 
  scale_x_discrete(labels = c(
    "grasping" = "Grasping",
    "multiple_objects" = "Multiple Objects",
    "depth_navigation" = "Depth Navigation"
  )) +
  theme_minimal()
success_task

#ggsave(paste0(base_dir,"/plots/success.jpeg"), plot = success_task, dpi = 600)
```

#### Duration

```{r}
data %>%
  filter(outcome == 'succuess') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  group_by(task) %>% 
  summarize(mean = mean(navigation_duration, na.rm = TRUE),
            sd = sd(navigation_duration, na.rm = TRUE)) %>% 
  arrange(factor(task, levels = c("grasping", "multiple_objects", "depth_navigation")))

data %>%
  filter(outcome == 'succuess') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  group_by(group, task) %>% 
  summarize(mean = mean(navigation_duration, na.rm = TRUE),
            sd = sd(navigation_duration, na.rm = TRUE)) %>% 
  arrange(factor(task, levels = c("grasping", "multiple_objects", "depth_navigation")))

data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = as.factor(participant_id), y = navigation_duration, fill = task, alpha = group)) +
  geom_boxplot(outlier.shape = NA, color = "black") +  # Boxplot without outliers
  geom_jitter(width = 0.2, size = 1, alpha = 0.5) +  # Jittered points for individual data
  labs(title = "Navigation Duration per Participant and Task\n",
       x = "\nParticipant",
       y = "Navigation Duration (s)\n",
       fill = "Task") +
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +
  scale_fill_discrete(labels = c("grasping" = "Grasping",
                                 "multiple_objects" = "Multiple Objects",
                                 "depth_navigation" = "Depth Navigation")) +
  theme_minimal() +
  facet_wrap(~ group, scales = "free_x")
```

#### Detection Rate

```{r}
data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome = factor(outcome, levels = c('success', 'participant_fail'))) %>% 
  group_by(outcome) %>% 
  summarise(mean = mean(detection_rate, na.rm = TRUE),
            sd = sd(detection_rate, na.rm = TRUE))

data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome = factor(outcome, levels = c('success', 'participant_fail'))) %>% 
  group_by(outcome, group) %>% 
  summarise(mean = mean(detection_rate, na.rm = TRUE),
            sd = sd(detection_rate, na.rm = TRUE))


detections_outcome <- data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome = factor(outcome, levels = c('success', 'participant_fail'))) %>%
  ggplot(aes(x = outcome, y = detection_rate, color = group)) +
  geom_violin(#aes(fill = group), # optional
              position = position_dodge(width = 1), width = 1) +
  geom_boxplot(position = position_dodge(width = 1), 
               aes(color = group), # aes(color = group) for white boxes, aes(fill = group) for colored boxes
               #color = "black", # only if aes(fill = group)
               width = 0.08, # width = 0.08 with violin
               outlier.shape = NA) + 
  scale_fill_manual(values = c("Expert" = "#f7c674", "Naive" = "#3e8dcf")) + # boxplot colors
  geom_jitter(position = position_jitterdodge(jitter.width = 0.2, dodge.width = 1), size = 1, alpha = 0.35) +
  scale_color_manual(values = c("Expert" = "#fdb338", "Naive" = "#0475d4")) + # jitter colors
  labs(title = "Detection Percentage by Outcome\n",
       x = NULL,
       y = "Detections (%)\n",
       color = "Expertise",
       #fill = "Expertise" # if boxplots filled with color
       ) +  
  scale_x_discrete(labels = c("success" = "Success", "participant_fail" = "Fail")) +
  #coord_cartesian(ylim = c(0.7, 1.0)) +
  theme_minimal()
detections_outcome

#ggsave(paste0(base_dir,"/plots/detections.jpeg"), plot = detections_outcome, dpi = 600)
```
```{r}
data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome = factor(outcome, levels = c('success', 'participant_fail'))) %>% 
  group_by(outcome, task) %>% 
  summarise(mean = mean(detection_rate, na.rm = TRUE),
            sd = sd(detection_rate, na.rm = TRUE)) %>% 
  arrange(factor(task, levels = c("grasping", "multiple_objects", "depth_navigation")))

data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome = factor(outcome, levels = c('success', 'participant_fail'))) %>% 
  group_by(outcome, group, task) %>% 
  summarise(mean = mean(detection_rate, na.rm = TRUE),
            sd = sd(detection_rate, na.rm = TRUE)) %>% 
  arrange(factor(task, levels = c("grasping", "multiple_objects", "depth_navigation")))

data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = outcome, y = detection_rate, color = group)) +
  geom_boxplot(aes(fill = group), alpha = 0.5, outlier.shape = NA, color = "black") +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.3, dodge.width = 0.75), 
              size = 2, alpha = 0.7) +
  labs(title = "Detection Rate by Outcome and Task\n",
       x = NULL,
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  scale_x_discrete(labels = c("participant_fail" = "Fail", "success" = "Success")) +
  #coord_cartesian(ylim = c(0.7, 1.0)) +
  facet_wrap(~ task, scales = "fixed", labeller = labeller(
    task = c(
      "grasping" = "Grasping", 
      "multiple_objects" = "Multiple Objects", 
      "depth_navigation" = "Depth Navigation"
    )
  )) +
  theme_minimal()
```

#### Miscelleaneous

```{r}
data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome = factor(outcome, levels = c('success', 'participant_fail'))) %>%
  ggplot(aes(x = outcome, y = detection_rate, color = group)) +
  #geom_violin(position = position_dodge(width = 1), width = 1) +
  geom_boxplot(position = position_dodge(width = 1), 
               aes(fill = group), # aes(color = group) for white boxes
               color = "black", # only if aes(fill = group)
               #width = 0.08, # width = 0.08 with violin
               outlier.shape = NA) + 
  scale_fill_manual(values = c("Expert" = "#f7c674", "Naive" = "#3e8dcf")) + # boxplot colors
  geom_jitter(position = position_jitterdodge(jitter.width = 0.2, dodge.width = 1), 
              size = 2, # size = 1 for violin, size = 2 for boxplot only
              alpha = 0.35) +
  scale_color_manual(values = c("Expert" = "#fdb338", "Naive" = "#0475d4")) + # jitter colors
  labs(title = "Detection Percentage by Outcome\n",
       x = NULL,
       y = "Detections (%)\n",
       color = "Expertise",
       fill = "Expertise" # if boxplots filled with color
       ) +  
  scale_x_discrete(labels = c("success" = "Success", "participant_fail" = "Fail")) +
  coord_cartesian(ylim = c(0.7, 1.0)) +
  theme_minimal()
```


```{r}
data %>%
  filter(task == "grasping") %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  group_by(participant_id, task, group) %>%
  summarize(success_count = sum(outcome == 'success'), .groups = "drop") %>%
  ggplot(aes(x = as.factor(participant_id), y = (success_count / n_trials) * 100, fill = task, alpha = group)) +  
  geom_col(width = 0.75, position = "dodge", color = "black") +
  geom_text(aes(label = round((success_count / n_trials) * 100, 2)),  
            position = position_dodge(width = 0.75), vjust = 1.5, size = 3) +
  labs(title = "Success Percentage for Grasping Task\n",  
       x = "\nParticipant",  
       y = "Success (%)\n",  
       fill = "Task") +  
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +  
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +  
  scale_fill_manual(values = c("grasping" = hex[1]), guide = "none") +
  theme_minimal() +  
  facet_wrap(~ group, scales = "free_x")
```
```{r}
data %>%
  filter(task == "multiple_objects") %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  group_by(participant_id, task, group) %>%
  summarize(success_count = sum(outcome == 'success'), .groups = "drop") %>%
  ggplot(aes(x = as.factor(participant_id), y = (success_count / n_trials) * 100, fill = task, alpha = group)) +  
  geom_col(width = 0.75, position = "dodge", color = "black") +
  geom_text(aes(label = round((success_count / n_trials) * 100, 2)),  
            position = position_dodge(width = 0.75), vjust = 1.5, size = 3) +
  labs(title = "Success Percentage for Multiple Objects Task\n",  
       x = "\nParticipant",  
       y = "Success (%)\n",  
       fill = "Task") +  
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +  
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +  
  scale_fill_manual(values = c("multiple_objects" = hex[2]), guide = "none") +
  theme_minimal() +  
  facet_wrap(~ group, scales = "free_x")
```
```{r}
data %>%
  filter(task == "depth_navigation") %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  group_by(participant_id, task, group) %>%
  summarize(success_count = sum(outcome == 'success'), .groups = "drop") %>%
  ggplot(aes(x = as.factor(participant_id), y = (success_count / n_trials) * 100, fill = task, alpha = group)) +  
  geom_col(width = 0.75, position = "dodge", color = "black") +
  geom_text(aes(label = round((success_count / n_trials) * 100, 2)),  
            position = position_dodge(width = 0.75), vjust = 1.5, size = 3) +
  labs(title = "Success Percentage for Depth Navigation Task\n",  
       x = "\nParticipant",  
       y = "Success (%)\n",  
       fill = "Task") +  
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +  
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +  
  scale_fill_manual(values = c("depth_navigation" = hex[3]), guide = "none") +
  theme_minimal() +  
  facet_wrap(~ group, scales = "free_x")
```


```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  group_by(participant_id, task, group) %>%
  summarize(success_count = sum(outcome == 'success'), .groups = "drop") %>%
  ggplot(aes(x = as.factor(participant_id), y = (success_count / n_trials) * 100, fill = task, alpha = group)) + 
  geom_col(width = 0.75, position = "dodge", color = "black") +
  geom_text(aes(label = round((success_count / n_trials) * 100, 2)), 
            position = position_dodge(width = 0.75), vjust = 1.5, size = 3) +
  labs(title = "Success Percentage per Participant and Task\n", 
       x = "\nParticipant", 
       y = "Success (%)\n",
       fill = "Task") +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +
  scale_fill_discrete(labels = c("grasping" = "Grasping", 
                                 "multiple_objects" = "Multiple Objects", 
                                 "depth_navigation" = "Depth Navigation")) +
  theme_minimal() +
  facet_wrap(~ group, scales = "free_x")
```


DURATION

```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome_color = ifelse(outcome == "success", task, "failure")) %>%  # Define color variable
  ggplot(aes(x = as.factor(participant_id), y = navigation_duration, fill = task, alpha = group)) +
  geom_boxplot(outlier.shape = NA, color = "black") +  # Boxplot without outliers
  geom_jitter(position = position_jitterdodge(jitter.width = 0.25, dodge.width = 0.75), size = 1, alpha = 0.7) +  # Jittered points
  labs(title = "Navigation Duration per Participant and Task\n",
       x = "\nParticipant",
       y = "Navigation Duration (s)\n",
       fill = "Task",
       color = "Outcome") +  # Legend for success/failure points
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +
  scale_color_manual(values = c("grasping" = "#F8766D",   # Keep task colors
                                "multiple_objects" = "#00BA38",
                                "depth_navigation" = "#619CFF",
                                "failure" = "red")) +  # Failure trials in red
  scale_fill_discrete(labels = c("grasping" = "Grasping",
                                 "multiple_objects" = "Multiple Objects",
                                 "depth_navigation" = "Depth Navigation")) +
  #scale_y_continuous(limits = c(0, 40), breaks = seq(0, 40, by = 10)) +  # Y-axis limit to 40s
  theme_minimal() +
  facet_wrap(~ group, scales = "free_x")
```

```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome_color = ifelse(outcome == "success", task, "failure")) %>%  # Define color variable
  ggplot(aes(x = as.factor(participant_id), y = navigation_duration, fill = task, alpha = group)) +
  geom_boxplot(outlier.shape = NA, color = "black") +  # Boxplot without outliers
  #geom_jitter(aes(color = outcome_color), width = 0.2, size = 1, alpha = 0.8) +  # Jittered points
  geom_jitter(position = position_jitterdodge(jitter.width = 0.25, dodge.width = 0.75), size = 1, alpha = 0.7) +  # Jittered points
  labs(title = "Navigation Duration per Participant and Task\n",
       x = "\nParticipant",
       y = "Navigation Duration (s)\n",
       fill = "Task",
       color = "Outcome") +  # Legend for success/failure points
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +
  scale_color_manual(values = c("grasping" = "#F8766D",   # Keep task colors
                                "multiple_objects" = "#00BA38",
                                "depth_navigation" = "#619CFF",
                                "failure" = "red")) +  # Failure trials in red
  scale_fill_discrete(labels = c("grasping" = "Grasping",
                                 "multiple_objects" = "Multiple Objects",
                                 "depth_navigation" = "Depth Navigation")) +
  coord_cartesian(ylim = c(0, 40)) +  # Zoom-in effect without affecting data
  theme_minimal() +
  facet_wrap(~ group, scales = "free_x")
```

```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
         outcome_color = ifelse(outcome == "success", task, "failure")) %>%  # Define color variable
  ggplot(aes(x = as.factor(participant_id), y = navigation_duration, fill = task, alpha = group)) +
  geom_boxplot(outlier.shape = NA, color = "black") +  # Boxplot without outliers
  labs(title = "Navigation Duration per Participant and Task\n",
       x = "\nParticipant",
       y = "Navigation Duration (s)\n",
       fill = "Task",
       color = "Outcome") +  # Legend for success/failure points
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 0.75), guide = "none") +
  scale_color_manual(values = c("grasping" = "#F8766D",   # Keep task colors
                                "multiple_objects" = "#00BA38",
                                "depth_navigation" = "#619CFF",
                                "failure" = "red")) +  # Failure trials in red
  scale_fill_discrete(labels = c("grasping" = "Grasping",
                                 "multiple_objects" = "Multiple Objects",
                                 "depth_navigation" = "Depth Navigation")) +
  coord_cartesian(ylim = c(0, 40)) +  # Zoom-in effect without affecting data
  theme_minimal() +
  facet_wrap(~ group, scales = "free_x")
```

Above plot may be reserve plot if we need more visuals.

```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%  # Define color variable
  ggplot(aes(x = as.factor(participant_id), y = navigation_duration, fill = task, alpha = group)) +
  geom_boxplot(outlier.shape = NA, color = "black") +
  labs(title = "Navigation Duration per Participant and Task\n",
       x = "\nParticipant",
       y = "Navigation Duration (s)\n",
       fill = "Task",
       color = "Outcome") +  # Legend for success/failure points
  scale_alpha_manual(values = c("Expert" = 1, "Naive" = 1), guide = "none") +
  scale_color_manual(values = c("grasping" = "#F8766D",   # Keep task colors
                                "multiple_objects" = "#00BA38",
                                "depth_navigation" = "#619CFF")) +
  scale_fill_discrete(labels = c("grasping" = "Grasping",
                                 "multiple_objects" = "Multiple Objects",
                                 "depth_navigation" = "Depth Navigation")) +
  coord_cartesian(ylim = c(0, 40)) +  # Zoom-in effect without affecting data
  theme_minimal() +
  facet_wrap(~ group, scales = "free_x")
```


```{r}
data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = outcome, y = detection_rate, color = group)) +
  geom_boxplot(aes(fill = group), alpha = 0.5, outlier.shape = NA, color = "black") +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.3, dodge.width = 0.75), size = 2, alpha = 0.7) +
  labs(title = "Detection Rate by Outcome\n",
       x = NULL,
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  scale_x_discrete(labels = c("participant_fail" = "Fail", "success" = "Success")) +
  coord_cartesian(ylim = c(0.7, 1.0)) +  # Zoom-in effect without affecting data
  theme_minimal()
```

Interpretation: First of all there seems to be a larger spread in DR for naive Ps than for Experts indicating that experts are able to better make use of the bracelet's information while also incorporating knowledge about the camera positioning. In more detail, detections get lost either when P moves the head to much such that camera FOV is not able to capture the target object anymore, or when hand movements are too fast (?) Further, there seems to be a higher correlation between DR and outcome for naive Ps than for experts, indicating that either naive Ps have a higher success rate due to higher detection rates or less failures are caused by generally higher detection rates, i.e. in failure trials naive Ps may have moved head to fast (or hand), especially upon grasping signal, causing an alternation of the direction from hand to target.

- larger spread -> training not that efficient (camera pos essential)

```{r}
data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = outcome, y = detection_rate, color = group)) +
  geom_boxplot(aes(fill = group), alpha = 0.5, outlier.shape = NA, color = "black") +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.3, dodge.width = 0.75), 
              size = 2, alpha = 0.7) +
  labs(title = "Detection Rate by Outcome and Task\n",
       x = NULL,
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  scale_x_discrete(labels = c("participant_fail" = "Fail", "success" = "Success")) +
  #coord_cartesian(ylim = c(0.7, 1.0)) +
  facet_wrap(~ task, scales = "fixed", labeller = labeller(
    task = c(
      "grasping" = "Grasping", 
      "multiple_objects" = "Multiple Objects", 
      "depth_navigation" = "Depth Navigation"
    )
  )) +
  theme_minimal()
```

```{r}
data %>%
  filter(outcome == 'success' | outcome == 'participant_fail') %>% 
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = outcome, y = detection_rate, color = group)) +
  geom_boxplot(aes(fill = group), alpha = 0.5, outlier.shape = NA, color = "black") +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.3, dodge.width = 0.75), 
              size = 2, alpha = 0.7) +
  labs(title = "Detection Rate by Outcome and Task\n",
       x = NULL,
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  scale_x_discrete(labels = c("participant_fail" = "Fail", "success" = "Success")) +
  coord_cartesian(ylim = c(0.7, 1.0)) +
  facet_wrap(~ task, scales = "fixed", labeller = labeller(
    task = c(
      "grasping" = "Grasping", 
      "multiple_objects" = "Multiple Objects", 
      "depth_navigation" = "Depth Navigation"
    )
  )) +
  theme_minimal()
```

DURATION

```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = navigation_duration, y = detection_rate, color = group)) +
  geom_jitter(size = 2, alpha = 0.3, width = 0.5, height = 0.01) +  # Jittered points to avoid overlap
  geom_smooth(method = "loess", se = TRUE, aes(fill = group), alpha = 0.2) +  # Smoothed trend lines with confidence interval
  labs(title = "Detection Rate vs. Navigation Duration\n",
       x = "Navigation Duration (s)\n",
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  theme_minimal()
```

```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = navigation_duration, y = detection_rate, color = group)) +
  geom_jitter(size = 2, alpha = 0.3, width = 0.5, height = 0.01) +  # Jittered points to avoid overlap
  geom_smooth(method = "loess", se = TRUE, aes(fill = group), alpha = 0.2) +  # Smoothed trend lines with confidence interval
  labs(title = "Detection Rate vs. Navigation Duration\n",
       x = "Navigation Duration (s)\n",
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  coord_cartesian(xlim = c(0, 40)) +
  theme_minimal()
```

- reserve plot ?

```{r}
data %>%
  mutate(group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive")) %>%
  ggplot(aes(x = navigation_duration, y = detection_rate, color = outcome, shape = group)) + 
  geom_jitter(size = 2, alpha = 0.5, width = 0.5, height = 0.01) +  # Jittered points to prevent overlap
  geom_smooth(method = "loess", se = TRUE, aes(fill = group, color = group), alpha = 0.2) +  # Smoothed trend lines per expertise
  labs(title = "Detection Rate vs. Navigation Duration\n",
       x = "Navigation Duration (s)\n",
       y = "Detection Rate\n",
       color = "Outcome", shape = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("success" = "green", "participant_fail" = "red", 
                                "Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  coord_cartesian(xlim = c(0, 25)) +
  theme_minimal()
```

As except one trial, most fails appeared at rather higher detection rates, we could say that failure is independent of DR and thus training is the major factor between the outcome of experts vs outcome of naive Ps.

- reserve? only one for DR vs duration (simple)

```{r}
data %>%
  mutate(
    group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
    task = factor(task, levels = c("grasping", "multiple_objects", "depth_navigation"))
  ) %>%
  ggplot(aes(x = navigation_duration, y = detection_rate, color = group)) +
  geom_jitter(size = 2, alpha = 0.3, width = 0.5, height = 0.01) +  # Jittered points to avoid overlap
  geom_smooth(method = "loess", se = TRUE, aes(fill = group), alpha = 0.2) +  # Smoothed trend lines with confidence interval
  labs(title = "Detection Rate vs. Navigation Duration\n",
       x = "Navigation Duration (s)\n",
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  facet_wrap(~ task, scales = "free_x", labeller = labeller(task = c(
    "grasping" = "Grasping", 
    "multiple_objects" = "Multiple Objects", 
    "depth_navigation" = "Depth Navigation"
  ))) +
  #coord_cartesian(xlim = c(0, 40)) +
  theme_minimal()
```

Zoomed in to xE[0,30].

```{r}
data %>%
  mutate(
    group = ifelse(participant_id %in% c(1, 2), "Expert", "Naive"),
    task = factor(task, levels = c("grasping", "multiple_objects", "depth_navigation"))
  ) %>%
  ggplot(aes(x = navigation_duration, y = detection_rate, color = group)) +
  geom_jitter(size = 2, alpha = 0.3, width = 0.5, height = 0.01) +  # Jittered points to avoid overlap
  geom_smooth(method = "loess", se = TRUE, aes(fill = group), alpha = 0.2) +  # Smoothed trend lines with confidence interval
  labs(title = "Detection Rate vs. Navigation Duration\n",
       x = "Navigation Duration (s)\n",
       y = "Detection Rate\n",
       color = "Expertise", fill = "Expertise") +  
  scale_color_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +  
  scale_fill_manual(values = c("Expert" = "darkblue", "Naive" = "lightblue")) +
  facet_wrap(~ task, scales = "free_x", labeller = labeller(task = c(
    "grasping" = "Grasping", 
    "multiple_objects" = "Multiple Objects", 
    "depth_navigation" = "Depth Navigation"
  ))) +
  coord_cartesian(xlim = c(0, 30)) +
  theme_minimal()
```

