---
title: "OptiVisT AIBox Grasping Task Analysis"
author: "Florian Pätzold"
date: "12/09/2024"
output:
  html_document: default
  pdf_document: default
---

# 1. Setup

Set up the document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE) # for debugging
```

Import all necessary packages.

```{r, echo=FALSE}
library(tidyverse) # ggplot2, tibble, tidyr, readr, purrr, dplyr, stringr, forcats
library(scales) # ggplot default color palette
library(e1071) # skewness and kurtosis
library(ggcorrplot) # correlation
```

Load all the grasping data.

```{r}
# Set working directory to the folder containing the CSV files
base_dir <- getwd()
data_dir <- paste0(base_dir, "/grasping/")

# Get list of all CSV files for the grasping task in the folder
files <- list.files(data_dir, pattern = "*grasping_participant*")

data_raw <- data.frame()
for (file in files) {
  csv_data <- read_csv(paste0(data_dir,file))
  participant_id = str_sub(file, start = -5, end = -5)
  csv_data <- csv_data %>% mutate(participant_id = as.numeric(participant_id)) # here as num
  data_raw <- rbind(data_raw, csv_data)
}

# View sample of the combined data
data_raw %>% sample_n(10)
```

# 2. Data Preprocessing

## 2.1 Data Engineering

Rename the columns and set data type.

```{r}
# Coco labels for class-label conversion
coco_labels <- c(
  "person", "bicycle", "car", "motorcycle", "airplane", "bus", "train", "truck", "boat",
  "traffic light", "fire hydrant", "stop sign", "parking meter", "bench", "bird", "cat", 
  "dog", "horse", "sheep", "cow", "elephant", "bear", "zebra", "giraffe", "backpack", 
  "umbrella", "handbag", "tie", "suitcase", "frisbee", "skis", "snowboard", "sports ball", 
  "kite", "baseball bat", "baseball glove", "skateboard", "surfboard", "tennis racket", 
  "bottle", "wine glass", "cup", "fork", "knife", "spoon", "bowl", "banana", "apple", 
  "sandwich", "orange", "broccoli", "carrot", "hot dog", "pizza", "donut", "cake", "chair", 
  "couch", "potted plant", "bed", "dining table", "toilet", "tv", "laptop", "mouse", "remote", 
  "keyboard", "cell phone", "microwave", "oven", "toaster", "sink", "refrigerator", "book", 
  "clock", "vase", "scissors", "teddy bear", "hair drier", "toothbrush"
)
names(coco_labels) <- as.character(0:79)

# Number of participants and trials
n_participants <- max(data_raw$participant_id) # 4
n_trials <- 10

data_reconstructed <- data_raw %>% 
  mutate(participant_id = as.factor(participant_id),
         trial = as.factor(rep(1:10, n_participants)),
         target = coco_labels[as.character(`0`)],
         start_time = as.numeric(`1`),
         navigation_time = as.numeric(`2`),
         freezing_time = as.numeric(`3`),
         grasping_time = as.numeric(`4`),
         end_time = as.numeric(`5`),
         key = as.character(`6`),
         detection = `7`,
         confidence = `8`,
         class_track_ids = `9`,
         target_track_id = `10`,
         target_position = `11`) %>% 
  select(participant_id, trial, target, key, 
         start_time, navigation_time, freezing_time, grasping_time, end_time, 
         detection, confidence, target_position, target_track_id, class_track_ids)

# Save the combined data frame as a CSV file
write.csv(data_reconstructed, paste0(data_dir,"combined_grasping.csv"), row.names = FALSE)

# View the engineered data
data_reconstructed
```

```{r}
detection_frame_drop_threshold = 10 # ~40fps average --> 0.25s

data_engineered <- data_reconstructed %>% 
  select(participant_id, trial, target, key, start_time, navigation_time, freezing_time, grasping_time, end_time, detection, confidence) %>% 
  mutate(
    outcome = ifelse(key == 'y', "success", 
              ifelse(key == 'n', "participant_fail", 
              ifelse(key == 'f', "navigation_fail", 
              ifelse(key == 't', "detection_fail", "aborted")))),
              
    trial_duration = end_time - start_time,
    navigation_duration = grasping_time - navigation_time,
    freezing_onset_duration = grasping_time - freezing_time,
    
    # Convert detection to numeric and compute detection rate
    detection = lapply(detection, function(x) as.numeric(unlist(strsplit(x, ",")))),
    detection_rate = sapply(detection, function(x) if (length(x) > 0) sum(x, na.rm = TRUE) / length(x) else NA),
    
    # Count detection drops if lost for X consecutive frames
    detection_drops = sapply(detection, function(x) sum(rle(x == 0)$lengths >= detection_frame_drop_threshold, na.rm = TRUE)),
    
    # Convert confidence to numeric and compute average
    confidence = lapply(confidence, function(x) as.numeric(unlist(strsplit(x, ",")))),
    confidence_average = sapply(confidence, function(x) mean(x[x>0], na.rm = TRUE))
  )

# freezing_time and grasping_time seem to be the same resulting in always 0 for freezing_onset_duration, so we remove it
data_engineered <- data_engineered %>% select(participant_id, trial, target, outcome, trial_duration, navigation_duration, confidence_average, detection_drops, detection_rate)
data_engineered
```

## 2.2 Data Cleaning

We will detect and treat missing values as well as technical false measurements.

```{r}
n_uncleaned <- nrow(data_engineered)

outliers <- rbind(
  data_engineered %>% filter_if(is.numeric, any_vars(is.na(.))), 
  data_engineered %>% filter_if(is.numeric, any_vars(is.infinite(.))),  # Detect infinite values in numeric columns
  data_engineered %>% filter(participant_id < 0),  # No negative participant IDs
  data_engineered %>% filter(trial < 0 | trial > 10),  # No negative trial numbers, and no more than 10
  data_engineered %>% filter(trial_duration < 0)  # Negative trial durations are measurement errors
)
outliers

# Treatment
data <- data_engineered %>% anti_join(outliers, by = colnames(data_engineered))

n_cleaned <- nrow(data)
cat('Rows removed: ', n_uncleaned - n_cleaned)
data
```

# 3. Analysis

## 3.1 Exploration

### Visualizations

We will explore the data using visualizations and summary statistics.

Pre-load color palette.

```{r}
hex <- hue_pal()(8)
hex
show_col(hex)

# red: #F8766D
# orange: #C49A00
# olive: #93AA00
# green: #00BE67
# cyan: #00BFC4
# lightblue: #00B9E3
# darkblue: #619CFF
```

Navigation duration.

```{r}
# Visualize duration distribution
data %>% 
  mutate(participant_id = fct_recode(participant_id, 
                                     "Participant 1" = "1",
                                     "Participant 2" = "2",
                                     "Participant 3" = "3",
                                     "Participant 4" = "4")) %>%
  ggplot(aes(x = log(navigation_duration), fill = participant_id)) +
  geom_density(alpha=0.4) +
  labs(title = "Duration distribution by Participant\n",
       x = "\nDuration in log(s)",
       y = NULL) +
  theme_minimal() +
  theme(legend.title = element_blank())

# Visualize normality using QQ-plot
data %>% 
  ggplot(aes(sample = navigation_duration)) +
  geom_qq() +
  geom_qq_line(color = 'firebrick') +
  labs(title = "Q-Q Plots of Duration by Participant\n",
       x = "\nTheoretical Quantiles",
       y = "Sample Quantiles\n") +
  theme_minimal() +
  facet_wrap(~ participant_id)

# Optional: Shapiro-Wilk Test (Wilhelm, Jochen. (2020). Re: Use T test, transform data or use non parametric tests?. Retrieved from: https://www.researchgate.net/post/Use_T_test_transform_data_or_use_non_parametric_tests/5efd860f4397bc39891a1b98/citation/download. )
# Treatment: natural slight right-skewness [0,Inf] --> no treatment
```

The distribution of navigation duration highlights individual differences and especially underlines that the experimenters did not instruct Ps to be fast: P1&2 experts are not necessarily faster or more consistent than P3&4 naive participants. It therefore does not make sense to evaluate the bracelet in light of the Ps navigation durations, but only focus on trial outcome.

```{r}
# Navigation duration per participant
data %>% 
  ggplot(aes(x = participant_id, y = navigation_duration)) +
  geom_boxplot(fill = '#619CFF') +
  labs(title = "Navigation duration per participant\n",
       x = "\nParticipant",
       y = "Duration\n") +
  theme_minimal()

# Navigation duration per participant
data %>% 
  ggplot(aes(x = participant_id, y = log(navigation_duration))) +
  geom_boxplot(fill = '#619CFF') +
  labs(title = "Navigation duration per participant\n",
       x = "\nParticipant",
       y = "log(Duration)\n") +
  theme_minimal()

# Summary statistics for duration
data %>% 
  group_by(participant_id) %>% 
  summarise(
    min = min(navigation_duration), 
    median = median(navigation_duration), 
    mean = mean(navigation_duration), 
    max = max(navigation_duration), 
    skew = skewness(navigation_duration)
    )
```

```{r}
# Navigation durations over time (speed fatigue)
data %>% group_by(trial) %>% summarise(mean_duration = mean(navigation_duration)) %>% 
  ggplot(aes(x = as.numeric(trial), y = mean_duration)) + # as.numeric to add line between trials
  geom_point(color = '#619CFF') +
  geom_line(color = '#619CFF') +
  labs(title = "Mean Duration per Trial\n",
       x = "\nTrial",
       y = "Duration\n") +
  scale_x_continuous(
    breaks = c(seq(from = 0, to = 10, by = 1)),
    limits = c(1, 10)
    ) +
  theme_minimal()

data %>% 
  group_by(trial) %>% 
  summarise(
    min = min(navigation_duration), 
    median = median(navigation_duration), 
    mean = mean(navigation_duration), 
    max = max(navigation_duration), 
    skew = skewness(navigation_duration)
    )
```

```{r}
# Navigation duration as a function of detection confidence
data %>%
  ggplot(aes(x = confidence_average, y = navigation_duration)) +
  geom_point(color = '#619CFF') +
  geom_line(color = '#619CFF') +
  labs(title = "t ~ detection confidence\n",
       x = "\nX",
       y = "Navigation duration (s)\n") +
  theme_minimal()

# Navigation duration as a function of detection rate
data %>% 
  ggplot(aes(x = detection_rate, y = navigation_duration)) +
  geom_point(color = '#619CFF') +
  geom_line(color = '#619CFF') +
  labs(title = "t ~ detection rate\n",
       x = "\nX",
       y = "Navigation duration (s)\n") +
  theme_minimal()

# facet of predictors' effects
data %>%
  pivot_longer(cols = c(confidence_average, detection_rate),
               names_to = "predictor", values_to = "value") %>%
  ggplot(aes(x = value, y = navigation_duration), color = outcome) +
  geom_point(alpha = 0.4, color = "#619CFF") +  # Scatterplot
  geom_smooth(method = "lm", color = "black", se = TRUE) +  # Linear trend
  facet_wrap(~ predictor, scales = "free_x") +  # Separate panels for each predictor
  labs(title = "Effect of Predictors on Navigation Duration",
       x = NULL, y = "Navigation Duration") +
  theme_minimal()
```

Important: The participants were not instructed to move as fast as possible, but move in accordance with their convenience and rather cautious to correctly interpret signals. Therefore, the above predictors cannot convincingly tell us anything about navigation duration. This might be different for the success rate.

- detection_rate only
- group color code outcome on scatter


Success rates.

```{r}
# Differences between participants in success rates
data %>%
  group_by(participant_id) %>%
  summarize(success_count = sum(outcome == 'success')) %>%
  ggplot(aes(x = participant_id, y = (success_count/n_trials)*100)) +
  geom_col(color = 'black', fill = '#C49A00') +
  geom_text(aes(label = round((success_count/n_trials)*100, 2), vjust = 2)) +
  labs(title = "Success Rate per Participant\n",
       x = "\nParticipant",
       y = "Success Percentage\n") +
  scale_y_continuous(
    breaks = c(seq(from = 0, to = 100, by = 20)),
    limits = c(0, 100)
    ) +
  theme_minimal()

# Success rate histogram
data %>%
  mutate(outcome = ifelse(outcome == "success", "success", "fail")) %>%  # Group all failures as "fail"
  group_by(trial, outcome) %>%
  summarize(count = n(), .groups = "drop") %>%
  ggplot(aes(x = factor(trial), y = count, fill = outcome)) +  # factor(trial) ensures discrete x-axis
  geom_col(position = "fill", color = "black") +  # "fill" makes it 100% stacked bars
  scale_y_continuous(labels = scales::percent) +  # Convert y-axis to percentages
  scale_fill_manual(values = c("success" = "#7CAE00", "fail" = "#F8766D")) +  # Custom colors
  labs(title = "Success and Failure Proportions per Trial\n",
       x = "\nTrial",
       y = "Percentage\n",
       fill = "Outcome") +
  theme_minimal()
```

- color code experts / naive ?
- combine data -> all tasks in facet plot
- "rate" or "percentage"
- plot chance level: 20% or spatial percentage? --> not plot because debatable
- success percentage per participant, grouped by task and color code experts / naive OR split once

No visible learning effects within the condition.

```{r}
# success ~ detection confidence
data %>%
  ggplot(aes(x = outcome, y = confidence_average, fill = outcome)) +
  geom_violin(alpha = 0.5) +
  geom_jitter(width = 0.1, alpha = 0.5, color = "black") +
  labs(title = "Confidence Average by Outcome", x = "Outcome", y = "Confidence Average") +
  theme_minimal()

# detection confidence predictor model
data %>%
  mutate(success_numeric = ifelse(outcome == "success", 1, 0)) %>%
  ggplot(aes(x = confidence_average, y = success_numeric)) +
  geom_jitter(width = 0, height = 0.05, alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), color = "blue") +
  labs(title = "Probability of Success by Confidence Average", x = "Confidence Average", y = "Probability of Success") +
  theme_minimal()
```

```{r}
# success ~ detection rate
data %>%
  ggplot(aes(x = outcome, y = detection_rate, fill = outcome)) +
  geom_violin(alpha = 0.5) +
  geom_jitter(width = 0.1, alpha = 0.5, color = "black") +
  labs(title = "Detection Rate by Outcome", x = "Outcome", y = "Detection Rate") +
  theme_minimal()

# detection rate predictor model
data %>%
  mutate(success_numeric = ifelse(outcome == "success", 1, 0)) %>%
  ggplot(aes(x = detection_rate, y = success_numeric)) +
  geom_jitter(width = 0, height = 0.05, alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), color = "blue") +
  labs(title = "Probability of Success by Detection Rate", x = "Detection Rate", y = "Probability of Success") +
  theme_minimal()
```

- color code
- combine tasks ?
- expertise dependence 

```{r}
# facet of predictors' effects
data %>%
  mutate(outcome = ifelse(outcome == "success", "success", "fail")) %>%
  pivot_longer(cols = c(confidence_average, detection_rate),
               names_to = "predictor", values_to = "value") %>%
  ggplot(aes(x = outcome, y = value, fill = outcome)) +
  geom_boxplot() +
  facet_wrap(~ predictor, scales='free') +
  labs(title = "Effect of Predictors on Outcome\n", x = NULL, y = NULL) +
  theme_minimal()
```

Important: Outcome is categorical and therefore the predictors can only be used as classifiers, therefore missing a certain level of detail that would give valuable information. However, it looks like the rates are mainly correlating counter accordance with intuition, i.e. objects in fail trials were detected, tracked and re-identified more consistently than in success trials.

```{r}
# experts
data %>%
  filter(participant_id == 1 | participant_id == 2) %>% 
  mutate(outcome = ifelse(outcome == "success", "success", "fail")) %>%
  pivot_longer(cols = c(confidence_average, detection_rate),
               names_to = "predictor", values_to = "value") %>%
  ggplot(aes(x = outcome, y = value, fill = outcome)) +
  geom_boxplot() +
  facet_wrap(~ predictor) +
  labs(title = "Effect of Predictors on Outcome for Expert Participants\n", x = NULL, y = NULL) +
  theme_minimal()

# naive
data %>%
  filter(participant_id == 3 | participant_id == 4) %>% 
  mutate(outcome = ifelse(outcome == "success", "success", "fail")) %>%
  pivot_longer(cols = c(confidence_average, detection_rate),
               names_to = "predictor", values_to = "value") %>%
  ggplot(aes(x = outcome, y = value, fill = outcome)) +
  geom_boxplot() +
  facet_wrap(~ predictor) +
  labs(title = "Effect of Predictors on Outcome for Naive Participants\n", x = NULL, y = NULL) +
  theme_minimal()
```

No major differences. Largest difference is that naive Ps fail for even higher detection rates than expert Ps.


### Correlation

We will now investigate potential correlations between variables.

- success ~ confidence_average + detection_rate + tracking_rate + identification_rate
- navigation_duration ~ confidence_average + detection_rate + tracking_rate + identification_rate
- success & navigation_duration

```{r}
cor_data <- data %>%
  mutate(success = ifelse(outcome == "success", 1, 0)) %>% 
  select(success, navigation_duration, confidence_average, detection_rate)

# get correlation matrix
cor_matrix <- cor(cor_data, use = "complete.obs")
cor_matrix


ggcorrplot(cor_matrix, 
           method = "square",  # Use tiles instead of circles
           type = "lower",  # Show only the lower triangle
           lab = TRUE,  # Show correlation values inside tiles
           colors = c("red", "white", "blue"),  # Red = negative, Blue = positive
           show.legend = TRUE,  # Ensure legend is visible
           outline.color = "white") +  # Add white grid lines for better separation
  labs(title = "Correlation Heatmap") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),  # Remove "Var 1" and "Var 2"
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels
```

## 3.2 Confirmation

After EDA, we will formulate and test relevant hypotheses.

Group-level (t-test):

1) Duration difference between success and fail trials

2) Duration difference between experts (P1,2) and naive Ps (P3,4)
3) Success difference between experts and naive Ps

4) Duration difference between (im)perfect tracking_rate
5) Success difference between (im)perfect tracking_rate

6) Duration difference between (im)perfect identification_rate
7) Success difference between (im)perfect identification_rate

```{r}

```

Note: We skip that part as we did not formulate clear hypotheses and statistical testing with low sample size has minor relevance / low power.

# 4. Modeling

After group-level comparison tests, we can perform more complex hypothesis testing by modeling the navigation_duration (linear model) and success (classifier).

```{r}

```

Note: We did not explicitly tell Ps to perform fast, i.e. modeling performance in terms of speed does not make sense. Accuracy could be modeled but again, we only have few data points and the goal of this analysis is not to deeply investigate underlying mechanisms but proof of concept of the navigation system which is best validated using simple numbers.
